Twists of supersymmetric gauge theories

### 2020-01-08 paper.tex
continuing 4d N=2

We now address the rank $(1,1)$ twist.

@@

>>>>

We now address the rank $(1,1)$ twist.  This is more straightforward: we can understand it by dimensional reduction from the 5d holomorphic twist, this time in a non-invariant direction.

@@

\begin{proof}
We start with the 5d $\mc N=1$ holomorphic twist, as in Theorem \ref{5d_holo_twist_theorem}, and dimensionally reduce in one of the two non-invariant directions.  That is, we apply Proposition \ref{CS_diml_red_prop}.
\end{proof}
